---
title: "README"
author: "Al Sabay"
date: "6/25/2018"
output:
  html_document: default
  pdf_document: default
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(synthpop)

# read in original sample data (cleveland dataset from uci)
cols <- c("age", "sex", "chest_pain", "resting_bp", "cholesterol", "fast_sugar",
          "resting_ecg", "max_hrate", "exer_angina", "oldpeak", "slope", "ca_mavesel",
          "heart_def_status", "diag")

df_data <- read.csv("data/cleveland14_capstone.csv", header = FALSE)

colnames(df_data) <- cols

# recode diagnosis (diag) to 1 if heart disease exists, or 0 if no heart disease exists
df_data$diag[df_data$diag > 0] <- 1

# synthesisze a data set of 20,000 samples from cleveland dataset.
# drop.not.used = True (means don't use any original data in the synthesized df)
syn_cleveland <- syn(df_data, seed = 306, k = 20000, drop.not.used = TRUE)

# data frame with the synthetic data set
df_syn <- data.frame(syn_cleveland$syn)
# logistic regression summary
summary(glm(diag~age+sex+chest_pain+resting_bp+cholesterol+fast_sugar+
              resting_ecg+max_hrate+exer_angina+oldpeak+slope+ca_mavesel+heart_def_status, 
            data = df_syn, family = "binomial"))

# use synthetic data to fit logistic regression and compare to original logistic regression fit
summary(glm.synds(diag~age+sex+chest_pain+resting_bp+cholesterol+fast_sugar+
              resting_ecg+max_hrate+exer_angina+oldpeak+slope+ca_mavesel+heart_def_status, 
            data = syn_cleveland, family = "binomial"))

# comparison of percentages of observed vs synthetic data
s1 <- syn(df_data, seed = 306, k = 50000, drop.not.used = TRUE)

# logistic regression fit of synthetic data
s2 <- glm.synds(diag~age+sex+chest_pain+resting_bp+cholesterol+fast_sugar+
                  resting_ecg+max_hrate+exer_angina+oldpeak+slope+ca_mavesel+heart_def_status, 
                data = syn_cleveland , family = "binomial")
```
## Synthesizing Heart Disease Data for Machine Learning
In many data applications especially in the medical field, data often comes in small samples and always subject the HIPPAA Privacy Laws. Small data samples often don't meet Machine Learning needs due to its lack of volume. 

Using the Cleveland dataset ( from http://archive.ics.uci.edu/ml/datasets/heart+disease), this example shows how we can use the "synthpop" R package to produce anonymized data in volume for research purposes. Although the resulting synthesized data matches the "real" data characteristics, it must be clearly understood that the resulting Synthesized Data is not "real data" and use should be limited to research studies (for ex: Machine and or Deep Learning).


## Plots

```{r pressure, echo=FALSE}
compare(s1, df_data, vars = "age")
compare(s1, df_data, vars = "sex")
compare(s1, df_data, vars = "chest_pain")
compare(s1, df_data, vars = "resting_bp")
compare(s1, df_data, vars = "cholesterol")
compare(s1, df_data, vars = "fast_sugar")
compare(s1, df_data, vars = "resting_ecg")
compare(s1, df_data, vars = "max_hrate")
compare(s1, df_data, vars = "exer_angina")
compare(s1, df_data, vars = "oldpeak")
compare(s1, df_data, vars = "slope")
compare(s1, df_data, vars = "ca_mavesel")
compare(s1, df_data, vars = "heart_def_status")
compare(s1, df_data, vars = "diag")
```

